ED2 model notes

### 2019-01-31 analysis/paper/ed-notes.Rmd
PAPER: Add description of N decomposition limitation scheme

>>>>

Calculation of N immobilization factor (subroutine `resp_f_decomp`, in `dynamics/soil_respiration.f90`).

N decomposition limitation affects the decomposition fraction (`csite%f_decomp`).
If no limitation, this is set to 1.

If limitation, calculate similarly to plant (supply relative to demand):

```
#-- dynamics/soil_respiration.f90:L226
Lc = exp(-3 * structural_soil_L / structural_soil_C)

N_immobilization_demand = A_decomp * Lc * decay_rate_stsc * structural_soil_C *
  ((1 - r_stsc) / c2n_slow - 1 / c2n_structural)

f_decomp = N_immobil_supply_scale * mineralized_soil_N / 
  (N_immobilization_demand + N_immobil_supply_scale * mineralized_soil_N)
```

Whether N decomposition limitation is enabled also affects decay rate of slow carbon pool if using `DECOMP_SCHEME = 2`.
With N limitation, decay rate is 100.2 year^-1^; otherwise, 0.2 year^-1^.
